Two Problems for Sophistication

### 2015-01-21 Facticity/Facticity/paper.tex
...

\subsection{Boosting a model class by manipulating the numbering}

@@

Otherwise, we can bound
\begin{align*}
C^{\K,\psi}(m)&=C^{\K\psi}(i)=K^\phi(1^r0j)\\
&\ge K^\phi(j)-c' \ge K^\psi(j)+r+1-c'\\
&=K^\psi(f)+r+1-c'.
\end{align*}
Now choose $r=c''+\max\{K^\psi(\phi_0),c'-1\}$. Then substitution yields, for both cases, 
$K^\phi(f)\ge c''+K^\psi(f)$.

Combining the inequalities above, for any model $g\not\in\M'$, there is a model $f\in\M$ such that
\[\begin{split}
K^\phi(g)+C^g(x) &\ge K^\psi(g)+C^g(x)+c''\\
&\ge K^\phi(f)+C^f(x) -2c+c'' -|\bar0|.
\end{split}\]

By choosing $c''$ sufficiently large, we can ensure that the best representation is in $\M'$ for all $x\in\X$, which completes the proof.
\end{proof}

@@

\begin{proof}
Let $\psi$ \sdr{This should probably be $\phi$} be any default enumeration of the partial recursive prefix functions. Note that since $f$ is a prefix function, if $f$ is defined for input $\epsilon$ then it cannot be defined for any other input. Pick $f,x$ with $f(\epsilon)=x$. Note that $x$ can be computed from $f$ and a fixed program, so there is a $c$ such that $K(x)\le K(f)+c$. Vice versa, given any $x$ we can construct an index of $f$, since $\psi$ is an acceptable numbering. Therefore $|K(f)-K(x)|\le c$.

>>>>

\subsection{Boosting submodel by manipulating the numbering}

@@

Otherwise, we can bound
\begin{align*}
C^{\K,\psi}(m)&=C^{\K,\psi}(i)=C^{\K,\psi}(1^r0j)\\
&\ge C^{\K,\psi}(j)-c' \ge C^{\K,\phi}(j)+r+1-c'\\
&=C^{\K,\phi}(m)+r+1-c'.
\end{align*}
Now choose $r=c''+\max\left\{C^{\K,\psi}(\phi_0),c'-1\right\}$. Then substitution yields, for both cases, 
$C^{\K,\phi}(m)\ge c''+C^{\K,\psi}(m)$.

Combining the inequalities above, for any model $g\not\in\M'$, there is a model $f\in\M$ such that
\[\begin{split}
C^{\K,\psi}(g)+\min \{|y| : g(y) = x\} &\ge C^{\K,^\phi}(g)+\min\{|y| : g(y) = x\}+c''\\
&\ge C^{\K,\psi}(f)+\min \{|y| : f(y) = x\} -2c+c'' -|\bar0|.
\end{split}\]
By choosing $c''$ sufficiently large, we can ensure that the best representation is in $\M'$ for all $x\in\X$, which completes the proof.
\end{proof}

@@

\begin{proof}
Note that since $\phi_i$ is a prefix function, if $\phi_i$ is defined for input $\epsilon$ then it cannot be defined for any other input. Pick $i,x$ with $\phi_i(\epsilon)=x$. Note that $x$ can be computed from $i$ and a fixed program, so there is a $c$ such that $C^{\K, \phi}(x)\le C^{\K, \phi}(\phi_i)+c$. Vice versa, given any $x$ we can construct an index of $f$, since $\psi$ is an acceptable numbering. Therefore $|K(f)-K(x)|\le c$.
